Verifying Demonstrations

### 2019-02-19 paper/adversary-model.tex
Reduces to A1 only, adds discussion of A1, A2, A3 (fixes #164)

\begin{adversaries}
\item\label{in-system-adversary}
  \emph{In-system adversary}:
  The adversary maliciously controls \(W\).
  The adversary honest-but-curiously controls \(S\).
  The adversary only learns the protocol data --- \ie what is sent over the 
  channel, no auxiliary data\footnote{%
    By auxiliary data we mean any data outside of the protocol, \ie
    meta-data such as who is on the other side of the channel obtained
    as side information, \eg by face recognition or inference from address
    to identiy.
  }

\item\label{deanonymizing-storage-adversary}
  \emph{National eavesdropping adversary}:
  The situation is the same as in \cref{in-system-adversary}, but now the storage 
  \(S\) learns the protester \(P\)'s identity from an auxiliary channel.
  However, \(W\) still learns only the protocol data, no auxiliary data.

%\item\label{deanonymizing-witness-adversary}
%  \emph{Deanonymizing-witness adversary}:
%  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
%  that now \(W\) also learns \(P\)'s identity from an auxiliary channel.
\end{adversaries}

The in-system adversary (\cref{in-system-adversary}) represents an adversary 
that has no access to data from outside the system, \eg inferences that can be 
done from the communication layer (\eg IP-addresses mapped to physical 
identities), which means that it has only the protocol data at its disposal.

We find \cref{in-system-adversary} suitable when the protester and witness both 
move in a crowd and there is no way for the witness to decide exactly with whom 
he or she communicates with.
(The protesters could also simply wear masks.)
We consider this a fair model for our purposes: if the adversary can 
deanonymize the protesters \emph{at the physical location} and thus arrest 
them, the adversary can do that independently of whether the protesters use our 
protocol or not --- thus our protocol cannot make things worse in such a 
situation.

As to \(S\), \cref{in-system-adversary} corresponds to an adversary who cannot 
even observe the channel between \(P\) and \(S\), \eg when \(P\) uses tools 
such as Tor~\cite{Tor}.
The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
\(S\) learns it; \eg \(S\) is operated outside the adversary's jurisdiction and 
so the adversary cannot control \(S\), but since \(S\) provides public access 
the adversary can (possibly constantly) query it and learn things with little 
delay.
Note that the adversary is also allowed to submit data to \(S\) for storage, 
just like everyone else.

\Cref{deanonymizing-storage-adversary} is a stronger adversary.
Although the adversary cannot observe the channel between \(P\) and \(S\), the 
adversary can still learn the identity of \(P\).
\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
thus perform time-correlation attacks on messages on the network and events 
observed from \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(A\) learns 
the identity of \(P\) in the communication with \(S\).

%However, in some situations this might not be the case: \Eg if the crowd is not 
%dense the witness will likely see the face of the protester.
%If the witness is controlled by the adversary, then it is likely that the 
%witness can capture a picture of the face, which can be turned into an identity 
%through face recognition.
%There are various such scenarios leading to the adversary learning the 
%protester's identity, we capture this as 
%\cref{deanonymizing-witness-adversary}.

>>>>

The adversary maliciously controls \(W\).
The adversary honest-but-curiously controls \(S\).
The adversary only learns the protocol data --- \ie what is sent over the 
channel, no auxiliary data\footnote{%
  By auxiliary data we mean any data outside of the protocol, \ie
  meta-data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.
}

This adversary represents an adversary that has no access to data from outside 
the system, \eg inferences that can be made from the communication layer (\eg 
IP-addresses mapped to physical identities or face recognition), which means 
that it has only the protocol data at its disposal.
